Hierarchy Builder

### 2020-06-19 coqws/easychair.tex
Better sectioning

Remark we can write abstract statements combining successive signatures:
\begin{coqcode}
(* An example statement in the signature of an Abelian group G, combining 0 and -. *)
Check forall G : AbelianGrp.type, forall x : G, x - x = 0.
(* An example statement in the signature of a Semiring S, combining 0, +, and *.  *)
Check forall S : SemiRing.type, forall x : S, x * 1 + 0 = x.
(* An example statement in the signature of a Ring R, combining -, 1 and *.  *)
Check forall R : Ring.type, forall x y : R, x * - (1 * y) = - x * y.
\end{coqcode}

Now, we can equip $\mathbb{Z}$ with commutative monoid, abelian group and
semi ring instances, and \HB{} equips it automatically with the ring
one, because there is only one possible choice.

@@

For space constraints we omit the declaration of the dashed arrows in
Figure~\ref{fig:hierarchy}, which are Factories, i.e. alternative
ways of building the same structures, but from different inputs.

Factories are used to accommodate the insertion of intermediate
structures in a hierarchy without breaking user code, as well as to
implement shortcuts: e.g. the factory to build a \coq{Ring} from a
\coq{Type} (rightmost dashed arrow) can omit the commutativity axiom
of the addition, since it is implied by the other axioms.

>>>>

\paragraph{Usage} We can write abstract statements combining successive signatures:
\begin{coqcode}
(* An example statement in the signature of an Abelian group G, combining 0 and -. *)
Check forall G : AbelianGrp.type, forall x : G, x - x = 0.
(* An example statement in the signature of a Semiring S, combining 0, +, and *.  *)
Check forall S : SemiRing.type, forall x : S, x * 1 + 0 = x.
(* An example statement in the signature of a Ring R, combining -, 1 and *.  *)
Check forall R : Ring.type, forall x y : R, x * - (1 * y) = - x * y.
\end{coqcode}

We can also equip $\mathbb{Z}$ with commutative monoid, abelian group
and semi ring instances, and \HB{} equips it automatically with a ring
instance, because there is only one possible choice.

@@

\paragraph{Factories}
For space constraints we omit the declaration of the dashed arrows in
Figure~\ref{fig:hierarchy}, which are Factories, i.e. alternative
ways of building the same structures from different inputs.

Factories are used to allow the insertion of intermediate
structures in a hierarchy without breaking user code, as well as to
implement shortcuts: e.g. the factory to build a \coq{Ring} from a
\coq{Type} can omit the commutativity axiom
of the addition, since it is implied by the other axioms.
